A Study of Target Following with X-Ray Vision in Augmented Reality

### 2009-06-25 Paper/paper.tex

\begin{figure}[t]
	\centering
	\includegraphics[width=3in]{figures/view_comp.png}
	\caption{Sample user-view of AR simulation.  Top Hat is visible (non-occluded) in the doorway.  The augmented view overlays transparent red rectangles on the characters, indicating their location while occluded.}
\end{figure}

>>>>

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=7in]{figures/triple_view.png}
	\caption{Sample views of AR simulation.  Transparent red rectangles overlay the people, indicating their location.  \emph{Left:} A user view of Top Hat (non-occluded) in the doorway.   \emph{Middle:} Three distractor people are visible through a large window.  \emph{Right:} A typical user view of a corner occluding several people.}
\end{figure*}
